Model-Based CubeSat Flight-Software Architecture using a Docs-as-Code Approach

### 2022-12-08 manuscript.tex
deploy: 4e2f24b33fd0b7b71d8689cb78e8b40807185d05

The following PLACEHOLDER TABLE, PLACEHOLDER TABLE, and PLACEHOLDER TABLE are all automatically generated using the M30ML structure and injected directly into this article. Should any changes be made to the SeaLion architecture repository, the tables can be immediately regenerated for continous updates.

@@

>>>>

The following \ref{stakeholder-needs-mapping}, PLACEHOLDER TABLE, and PLACEHOLDER TABLE are all automatically generated using the M30ML structure and injected directly into this article. Should any changes be made to the SeaLion architecture repository, the tables can be immediately regenerated for continous updates.

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=.5\textwidth]{stakeholder-needs-mapping}
    \caption{a view describing mapping of stakeholders to stakeholder needs in UML}
    \label{stakeholder-needs-mapping}
\end{figure}
